fMRI by caveat

### 2023-03-21 paper.qmd
paper updated somewhat

---
title: "fMRI by caveat"
author: "Tomas Knapen"
toc: true
number-sections: true
highlight-style: pygments
bibliography: lib/export_2023-3-16.bib
csl: templates/nature.csl
format:
  html:
    code-fold: true
  pdf:
    geometry:
        - top=30mm
        - left=30mm
        - top=30mm
        - left=30mm
  docx: default
jupyter: python3
---

>>>>

---
title: "fMRI by caveat"
author: "Tomas Knapen"
toc: true
toc-depth: 2
number-sections: true
highlight-style: pygments
bibliography: lib/export_2023-3-16.bib
csl: templates/nature.csl
format:
  html:
    code-fold: true
    toc-location: left
    toc: true
    toc-depth: 2
    number-sections: true
  pdf:
    geometry:
        - top=30mm
        - left=30mm
        - top=30mm
        - left=30mm
  docx: default
jupyter: python3
---
